\section{Introduction}
%
Model-based diagnosis \citep{dekleer87diagnosing} uses system models
and sensor data to compute diagnostic hypotheses. These hypotheses
have a range of applications such as decision-making
\citep{feldman13genius}, repair, reconfiguration, troubleshooting,
testing, and others. While providing many benefits, model-based
diagnosis is expensive due to the need to obtain/construct good system
models. To amortize this high modeling cost, researchers develop and
use component libraries.
\par
A component may have several representations in a component
library. For example, a NAND-gate may be modeled as a system of
non-linear equations that govern the analogue electrical laws of the
gate, or its linear approximation or with the simple Boolean
expression $o \leftrightarrow \neg(i_1 \wedge i_2)$. Although one may
postulate that the best choice for a component model is the one that
most accurately represents the physics (in the case of the NAND-gate,
this would be the analogue electrical model), experiments show that
the result of this choice is sometimes hard to predict and is
dependent on the diagnostic context.
%\par
%It is not possible to generte a formal framework for successfully
%generating a model of the ``correct'' fidelity. The most common
%approach is to manually test different models and examine trade-offs.
\par
In this article we propose the novel approach of performing
diagnostics inference using component model
libraries consisting of multiple models of differing fidelity. 
%Model ensembles have been used successfully in
%machine learning \citep{brown2010ensemble,dietterich2000ensemble}, but
%have not been adopted in diagnostics inference.
%\par
We present an approach to automatically compose a global diagnosis model from different types of sub-models from a library, such that the  model  maximizes a given score metric over a set of diagnosis test cases.
We use a test-set of diagnostic scenarios for learning the optimal system model,
where the test-set is artificially generated (e.g., by simulation) and
contains a representative set of likely faults. The algorithm we
propose chooses component models that optimize some (weighted)
diagnostic metrics such as diagnostic accuracy (which is dual of
classification errors), isolation time, or computational complexity
\citep{feldman10empirical}. The output of the algorithm is a system
model that can be later used for on-line diagnosis.
\par
To illustrate the usability of our algorithm, consider a diagnostic
model of a crane. The model would contain parts such as electrical
motors and drives and a Programmable Logic Controller
(PLC). Non-linear electromechanical-models are most appropriate choice
for the moving parts, however modeling the PLC with non-linear
equations would result in a suboptimal diagnosis due to high
complexity. Further, high simulation accuracy does not necessarily
translate to high diagnostic accuracy. The algorithm we propose would
run a few diagnostic scenarios and then would discard the
high-fidelity PLC model and instead use the computationally simpler
Boolean/qualitative/state-machine components. By doing this, the
algorithm optimizes the diagnostic performance of an MBD solver on a
set of diagnostic test cases.
\par
Our contributions are as follows. We describe an algorithm for
learning models with components of variable fidelity.  We illustrate
our algorithm on a multiple-tank dynamic system benchmark, consisting of multiple tanks connected with valves. 

**NEW RESULTS****

Even for such a
small system the output of the algorithm is non-intuitive as it shows
that only two out of three components in the system that we study can
be replaced with linear analogues if we want to preserve diagnostic
accuracy. We empirically show that the choice of modeling abstraction
depends on the model topology and cannot be preconceived during the
design of the component library.
