\documentclass{ifacconf}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{graphicx}
\usepackage[dvips]{epsfig}
\usepackage{epsf}
\usepackage{times}
\usepackage{xspace}
\usepackage[shortcuts]{extdash}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{tabularx}
\usepackage{times}
%
\newtheorem{problem}{Problem}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{proposition}{Proposition}
%
\graphicspath{{figures/}}
%
\input{defs}
%
\begin{document}
%
\begin{frontmatter}
%
\title{Model-Based Diagnosis Using Component Model Ensembles\thanksref{footnoteinfo}}
%
\thanks[footnoteinfo]{Supported by SFI grant 12/RC/2289.}
%
\author[First]{Alexander Feldman}
\author[Second]{Gregory Provan}
\author[First]{Rui Abreu}
\author[First]{Johan de Kleer}
%
\address[First]{PARC Inc., Palo Alto, CA 94304, USA\\(e-mail: \{afeldman,dekleer,rui\}@parc.com)}
\address[Second]{Department of Computer Science, University College Cork, Cork, Ireland (e-mail: g.provan@cs.ucc.ie).}
%
\begin{abstract}
%
System models that are used in model-based diagnosis are often
composed of components. The systems of equations that represent each
component are drawn from component libraries. In these component
libraries, there may be multiple systems of equations per component
(component implementations). For example, a component may be modeled
as a non-linear system (high-fidelity model), linear system, and a
qualitative system (low-fidelity model). Choosing the right component
model for system diagnosis is a difficult task and requires a search
in the space of all possible component type combinations. In this
paper we propose a method that automates this task and computes a
system model that optimizes a set of diagnostic metrics in a set of
diagnostic scenarios. Initial experimental results show that having
linear models of some of the components in a system preserves the
diagnostic accuracy and isolation time while, at the same time,
improves the computational complexity and numerical stability.
%
\end{abstract}
\end{frontmatter}
%
\input{introduction}
\input{related}
\input{notation}
\input{algorithm}
\input{empirical}
\input{conclusions}
%
\bibliography{safeprocess15-ensembles}
%
\end{document}
